Lifting CDCL to Numerical Domains

### 2016-10-11 contributions.tex
minor

\section{Contributions}
In this paper, we make the following contributions.
\begin{enumerate}
\item We present a novel program analysis technique based on 
abstract conflict driven clause learning algorithm~\cite{dhk2013-popl}.
To this end, we present a procedure for lifting CDCL algorithm to 
richer lattice structure such as {\em interval} and {\em octagon} 
abstract domains.

\item To enable lifting of CDCL algorithm, we implement 
our own template-based numerical abstract domains that 
supports complementation property.  Our proposed technique 
is embodied in our tool called, {\em Titlis}.  To the best 
of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

\item  Experiments on a set of benchmarks drawn from bit-vector 
regression suite in sv-comp, numerical programs and few 
control-intensive benchmarks from hardware domain shows that 
the strict generalization of CDCL algorithm effectively combines 
the efficiency of abstract domains while being path-sensitive and 
bit-precise at the same time.  This is attributed to the intelligent 
decision heuristics which exploits the high-level structure of the 
problem combined with stronger deductions and clause learning 
mechanism aided by the richer abstract domains.
\end{enumerate}

>>>>

\section{Contributions}
In this paper, we make the following contributions.
\begin{enumerate}
\item We present a novel program analysis technique that 
lift CDCL algorithm to relational numerical abstract domains.   
Our proposed technique is embodied in our tool called, {\em Titlis}.  
To the best of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

\item  Experiments on a set of benchmarks drawn from bit-vector 
regression suite in sv-comp, numerical programs and few 
control-intensive benchmarks from hardware domain shows that 
the strict generalization of CDCL algorithm effectively combines 
the efficiency of abstract domains while being path-sensitive and 
bit-precise at the same time.  
\end{enumerate}

### 2016-10-11 introduction.tex
minor

Clause learning SAT solvers requires a weak complementation property 
of the partial assignments domain.  However,  the most commonly 
used APRON~\cite{apron} library that implements abstract domains, is specialized 
for abstract interpretation framework which does not require complementation 
operator.  Thus, we implement our own template-based numerical abstract 
domains that support complementation property.  Our proposed technique 
is embodied in our tool called, {\em Titlis}.  To the best of our 
knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

>>>>

Clause learning SAT solvers requires a weak complementation property 
of the partial assignments domain.  However,  abstract domain 
library, such as APRON~\cite{apron}, is specialized for abstract 
interpretation framework which does not require complementation 
operator.  Thus, we implement our own template-based numerical abstract 
domains that support complementation property, required for clause learning 
in the domain.
